Accelerating Metagenomic Identification of DNA Sequences Using Artificial Neural Networks \todo{Taxonomic Classification znaczy coś innego}

### 2025-04-16 article/main.tex
poprawki, rn

    \todo{tutaj trzeba dac ogolny opis metody, moze rysunek, gdzie jest pokazane grupowanie, pytanie bazy danych itd}

@@

        % \subsection{Implementation Details}
        %     The solution consists of two components. The first is a library that contains components enabling the creation of pipelines for genetic material analysis in the form of taxonomic classification. The second component is a console application, which uses the library's components to allow for the creation and configuration of processing pipelines. Additionally, a web application was created, which allows users to submit analysis tasks through a web browser.

        %     The console application was implemented using the \textit{clap} library\cite{Rust:clap}. In library the $k$-medoid algorithm was provided by the \textit{kmedoids} library\cite{Rust:kmedoids}, and the neural network was built using the \textit{burn} library\cite{Rust:burn} with the \textit{wgpu} execution environment. Web application was implemented using the \textit{axum} library\cite{Rust:axum} with \textit{tokio}\cite{Rust:axum} async environment.

        %     Additionally, the following tools were used in the work:
        %     \begin{itemize}
        %         \item \textit{cargo} as the package manager and build system in Rust;
        %         \item \textit{rustup} for automatic management of Rust versions;
        %         \item \textit{clippy} for static code analysis in Rust;
        %         \item \textit{rustfmt} for automatic formatting of Rust source code;
        %         \item \textit{cargo test} for conducting unit tests;
        %         \item \textit{git} as the version control system, enabling change tracking and code history management.
        %     \end{itemize}

@@

@@

        \subsection{Classical approach}

>>>>

    \todo{opisać potok, jest tekst w pracy inżynierskiej;
      tutaj trzeba dac ogolny opis metody, moze rysunek, gdzie jest pokazane grupowanie, pytanie bazy danych itd}

@@

        \subsection{Implementation Details}
            The solution consists of two components. The first is a library that contains components enabling the creation of pipelines for genetic material analysis in the form of taxonomic classification. The second component is a console application, which uses the library's components to allow for the creation and configuration of processing pipelines. Additionally, a web application was created, which allows users to submit analysis tasks through a web browser.

            The console application was implemented using the \textit{clap} library\cite{Rust:clap}. In library the $k$-medoid algorithm was provided by the \textit{kmedoids} library\cite{Rust:kmedoids}, and the neural network was built using the \textit{burn} library\cite{Rust:burn} with the \textit{wgpu} execution environment. Web application was implemented using the \textit{axum} library\cite{Rust:axum} with \textit{tokio}\cite{Rust:axum} async environment.

            Additionally, the following tools were used in the work:
            \begin{itemize}
                \item \textit{cargo} as the package manager and build system in Rust;
                \item \textit{rustup} for automatic management of Rust versions;
                \item \textit{clippy} for static code analysis in Rust;
                \item \textit{rustfmt} for automatic formatting of Rust source code;
                \item \textit{cargo test} for conducting unit tests;
                \item \textit{git} as the version control system, enabling change tracking and code history management.
            \end{itemize}

@@

                \todo{wstep do badan, cel - zwiekszenie wydajnosci przy zachowaniu jakosci;
                  badania wymagaly 2 metod klasycznych; byly przeprowadzone na tych samych danych;}

@@

        \subsection{Base-line algorithms}
